The mass relations between supermassive black holes and their host galaxies at $1< z<2$ with \hst-WFC3

### 2019-06-06 manuscript/manuscript.tex
Before John's may edit

We include in our analysis published samples at intermediate redshift range to understand the redshift evolution of these correlations. We select samples that were analyzed by members of our team, in order to ensure uniform measurements. The intermediate redshift AGNs that we consider include, for the \mbh-\lhost\ relation, 52 objects published by \citet{Park15} at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11, SS13} at $0.5<z<1.9$. Moreover, \citet{Bennert11, SS13} also derive the \smass\ for the 27 objects which enable us to compare to the \mbh-\smass\ relation. We recalibrate the \mbh\ of the intermediate sample using the self-consistent recipes introduced in Section~\ref{mbh}.

@@

%Introduce the final inference using fitting:
The host properties of one AGN system is inferred via the following steps. First, we model the AGN and host using each PSFs in the library. Inputting the fitting ingredients to \lenstronomy, the posterior distribution of the parameter space is calculated and optimized by adopting the Particle Swarm Optimizer (PSO)\footnote{Note that, the \lenstronomy\ enables one to further infer the parametric confidence interval using MCMC. In our case, given a fixed PSF, the $1-\sigma$ inference of each parameter are extremely narrow. Thus, we only take the best-fit inference using PSO for the further calculations.}.
To avoid any unphysical inferences, we set the upper and lower limit for the key parameters as effective radius \Reff\ $\in[0\farcs{}1,1\farcs{0}]$, and \sersic\ index $n\in[1,7]$\footnote{{\color{blue}
%As will see, three AGN systems would have finally inference with abnormally high \sersic\ index value (i.e., $n>5$). We test to reanalyze these sample and fix the \sersic\ index within $n\in[1,4]$ and find their results changes very little ---  $\Delta$\lhost\ and $\Delta$\smass\ within 0.1 dex.
We test to use $n\in[1,4]$ as prior, and find that the changes on the inference of the host properties are very limited.
}}.
Then, we rank the performance of each PSF based on the $\chi^2$ value and select the top-eight PSFs as representative of the best fit PSFs. We infer the host \sersic\ parameters (i.e., host flux, \Reff, \sersic\ index) using a weighted arithmetic mean. The weight is calculated by:
\begin{eqnarray}
\label{eq:weights}
w_i = exp \big(- \alpha \frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2 \chi_{best} ^2} \big),
\end{eqnarray} 
where the $\alpha$ is an inflation parameter so that when $i=8$:
\begin{eqnarray}
\label{eq:alpha}
\alpha \frac{ \chi_{i=8} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2,
\end{eqnarray} 
The goal of this recipe is to weight each PSF based on their relative goodness of fit, while ensuring at least eight are used to capture the range of systematic uncertainties. The answers would not change significantly if we had chosen a different number of PSFs, as we show below.

@@

In Figure~\ref{fig:AGN_decomp}, we demonstrate the optimized results inferred by \lenstronomy, including the AGN images, best-fit models, image subtract point source (i.e. host) and the residuals, taking COSMOS-CID1174 as an example. The weights adopted in the analysis are listed in Table~\ref{tab:weight_CID1174}. In order to quickly overview our inference, we summarize the relations of the properties between effective radius \Reff, 2) \sersic\ index and 3) host to total flux ratio\footnote{We also comparing the distribution of the \sersic\ values to the inactive galaxies in the Appendix~\ref{sec:comp_inactive}.} in Figure~\ref{fig:flux_r_n_corner}.

@@

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_style1.pdf}}&
{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_style0.pdf}}\\
\end{tabular}
\caption{\label{fig:MM-vz} 
Left: illustration of the offset in log\mbh\ (VS. \smass) as a function of redshift. The orange band is the intrinsic scatter of local linear relation. Right: \mbh/\smass\ as a function of redshift. We use open green circle to show the expected shifting of the median offset value before and after consider the selection effect using framework by \citet{Schulze2011} in Section~\ref{sec:sf_framework}.
}
\end{figure*}

@@

\subsubsection{Test selection effect using Bayesian framework} \label{sec:sf_framework}
We use the Bayesian framework introduced by \citet{Schulze2011} to estimate the expected bias that could be raised by the selection window and local sample that we adopted. The framework considers the fact that, with the particular selection window, the intrinsic scatter in the BH-bulge relation has trend to decline regime of the stellar mass function, result in an average stellar masses lower than the relation. Moreover, the other relevant sources of bias are considered, for example the active fraction among SMBHs varies by the black hole mass function, in the sense that BHs with higher mass are less likely to be active than lower mass ones.

Considering our specific selection limits: $\log($\mbh$)~\in[7.5, 8.56]$, $\log(L_{\rm bol}) \in [45.0, 46.2] $ and  $\log(\lambda) \in [-2.0, 0.5]$, their is an expected bias of 0.21~dex in the inference of $\Delta\log($\mbh$)$ for samples at $z\sim1.5$. Interestingly, this bias could account for the offset that obtained in Section~\ref{sec:mm}. We use open green circle to point out the shifting of the expected population given the biases in Figure~\ref{fig:MM-vz}.

@@

{\color{blue}
\subsection{The origin of the offset}
{\color{red}[Xuheng:  Given their larger uncertainty, do we still want to present this?]}
We seek for the cause that could raise the evolution in the BH and host galaxy correlations at high redshift. We consider if the offset is related to the AGN activities. The straightforward way is to study such offset, i.e. $\Delta \log \mathcal M_{\rm BH}$, as a function of \mbh\ and Eddington ratios, showing in Figure~\ref{fig:offset_vs_MBH_edd}. Interestingly, we visually see the trend that the offset turns to be larger with at value of \mbh. However, at higher Eddington ratio, the offset turns to be lower.
 {\color{red} Some interpretations need to be presented.}

@@

\subsection{Systematic by different local anchor}
To compare our high-$z$ sample the local relation, we adopt the local measurements by \citet{Ben++10, Bennert++2011, H+R04} as the anchor at today. In the literature, there are other local measurements have been studied which could also be considered as the local anchor. We realize that the inconsistency in the different local samples shift our local anchor and thus changes the result of the co-evolutions.

For example, we compare our local \mbh-\smass\ sample to the local quiescent galaxies in \citet{Kormendy13} (hereafter K13). We find that K13's local \mbh-\smass\ relation would raise the anchor by $\sim$0.3~dex. This could mitigate our offset value $\gamma$ by 0.3~dex. However, we also note that the \mbh-\sigstar\ relations in K13 is also higher than the one by our local sample. Note that the \mbh-\sigstar\ relations by the quiescent galaxy are usually used to determine the virial coefficient for AGNs. That is, adopting the K13 would boost the value of our \mbh\ by $\sim$0.3~dex as well. As a result, our inference of the fitted offset $\gamma$ still remains at the same level.

@@

Combining out high-$z$ measurements with the intermediate redshift samples from the literature~\citep{Park15, Bennert11, SS13}, we compared the scaling relations to the ones by the local with main results summarized as follows:
\begin{enumerate}
\item The \mbh-\smass\ relations at higher redshift are inconsistent with the local ones, i.e. Figure~\ref{fig:MM}, \ref{fig:MM-vz}.
\item Considering the correction for passive evolution of galaxy luminosity, the \mbh-\lhost\ relations at higher redshift are inconsistent with the local ones,  i.e. Figure~\ref{fig:ML-vz}.
\item The offsets of by the evolution are well described by the form $\Delta\log\mathcal M_{\rm BH}= \gamma \log (1 + z)$. Taking intro account selection effect, we obtain $\gamma = 0.8\pm0.3$ (\mbh-\smass) and $\gamma = 0.6\pm0.3$ (\mbh-\lhost).
\item We compare the properties of our active galaxy sample to the ones from inactive galaxy in the CANDLES imaging survey at the same redshift range, finding no significant discrepancy among them.
\end{enumerate}

Our inference indicates the evidence of disk component, i.e. the ones with \sersic\ $n<2$, and the local comparing samples are bulge dominated sample, we hence conclude that the BHs 8-10~Gyrs ago reside in bulges, if not entire galaxies, which are less massive/luminous than today.

@@

The authors fully appreciate the discussions with Hyewon Suh, Vardha N. Bennert, Anton M. Koekemoer, Takahiro Morishita.

>>>>

We include in our analysis published samples at intermediate redshift range to understand the redshift evolution of these correlations. We select samples that were analyzed by members of our team, in order to ensure uniform measurements. The intermediate redshift AGNs that we consider include, for the \mbh-\lhost\ relation, 52 objects published by \citet{Park15} at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11, SS13} at $0.5<z<1.9$. Moreover, \citet{Bennert11, SS13} also derive the \smass\ for the 27 objects which enable us to compare to the \mbh-\smass\ relation. {\color{blue} In addition, we adopt a sample of 32 \mbh-\smass\ measurements at $0.3<z<0.9$ by \citet{Cisternas2011} to compare with our sample.

Across the intermediate redshift sample, we recalibrate the \mbh\ by \halpha\ or \hbeta\ using the self-consistent recipes introduced in Section~\ref{mbh}. For \mbh\ estimated by \Mgii\, we adopt the recipe by \citet{Ding2017b} to recalibrate them.
}

@@

%Introduce the final inference using fitting:
The host properties of one AGN system is inferred via the following steps. First, we model the AGN and host using each PSFs in the library. Inputting the fitting ingredients to \lenstronomy, the posterior distribution of the parameter space is calculated and optimized by adopting the Particle Swarm Optimizer (PSO)\footnote{Note that, the \lenstronomy\ enables one to further infer the parametric confidence interval using MCMC. In our case, given a fixed PSF, the $1-\sigma$ inference of each parameter are extremely narrow. Thus, we only take the best-fit inference using PSO for the further calculations.}.
To avoid any unphysical inferences, we set the upper and lower limit for the key parameters as effective radius \Reff\ $\in[0\farcs{}1,1\farcs{0}]$, and \sersic\ index $n\in[1,7]$\footnote{{\color{blue}
%As will see, three AGN systems would have finally inference with abnormally high \sersic\ index value (i.e., $n>5$). We test to reanalyze these sample and fix the \sersic\ index within $n\in[1,4]$ and find their results changes very little ---  $\Delta$\lhost\ and $\Delta$\smass\ within 0.1 dex.
We test to use $n\in[1,4]$ as prior to fit the systemic with high \sersic\ index ($n>4.5$), and find that the changes on the inference of their host magnitude are very limited ($<0.03$ dex).}
}.
Then, we rank the performance of each PSF based on the $\chi^2$ value and select the top-eight PSFs as representative of the best fit PSFs. We infer the host \sersic\ parameters (i.e., host flux, \Reff, \sersic\ index) using a weighted arithmetic mean. The weight is calculated by:
\begin{eqnarray}
\label{eq:weights}
w_i = exp \big(- \alpha \frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2 \chi_{best} ^2} \big),
\end{eqnarray} 
where the $\alpha$ is an inflation parameter so that when $i=8$:
\begin{eqnarray}
\label{eq:alpha}
\alpha \frac{ \chi_{i=8} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2,
\end{eqnarray} 
The goal of this recipe is to weight each PSF based on their relative goodness of fit, while ensuring at least eight are used to capture the range of systematic uncertainties. The answers would not change significantly if we had chosen a different number of PSFs, as we show below.

@@

In Figure~\ref{fig:AGN_decomp}, we demonstrate the optimized results inferred by \lenstronomy, including the AGN images, best-fit models, image subtract point source (i.e. host) and the residuals, taking COSMOS-CID1174 as an example. The weights adopted in the analysis are listed in Table~\ref{tab:weight_CID1174}. In order to quickly overview our inference, we summarize the relations of the properties between effective radius \Reff, 2) \sersic\ index and 3) host to total flux ratio in Figure~\ref{fig:flux_r_n_corner}. We also comparing the distribution of the \sersic\ values to the inactive galaxies in the Appendix~\ref{sec:comp_inactive}.

@@

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_style1.pdf}}&
{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_style0.pdf}}\\
\end{tabular}
\caption{\label{fig:MM-vz} 
Left: illustration of the offset in log\mbh\ (VS. \smass) as a function of redshift. The orange band is the intrinsic scatter of local linear relation. Right: \mbh/\smass\ as a function of redshift. 
{\color{blue} We use green open circles to show the expected shifting of the median value of the $\Delta$\mbh\ before and after consider the selection effect using framework by \citet{Schulze2011} in Section~\ref{sec:sf_framework}.}
{\color{red} [Xuheng: The blue points are from Cisternas et al. 2011, they are consistent to the local ones.]}
}
\end{figure*}

@@

\subsubsection{Test selection effect using Bayesian framework} \label{sec:sf_framework}
We use the Bayesian framework introduced by \citet{Schulze2011} to estimate the expected bias that could be raised by our selection window and local sample that adopted. Given the particular selection window (\mbh,  $L_{\rm bol}$ and Eddington ratio $\lambda$), the framework considers the fact that the intrinsic scatter in the BH-bulge relation has trend to decline regime of the stellar mass function, result in an average stellar masses lower than the relation. Moreover, the other relevant sources of bias are considered in this framework, for example the active fraction among SMBHs varies by the black hole mass function, in the sense that BHs with higher mass are less likely to be active than lower mass ones.

Considering our specific selection limits: $\log($\mbh$)~\in[7.5, 8.56]$, $\log(L_{\rm bol}) \in [45.0, 46.2] $ and  $\log(\lambda) \in [-2.0, 0.5]$, we infer an expected bias of 0.21~dex in the observed $\Delta\log($\mbh$)$ for samples at $z\sim1.5$. Interestingly, this bias could account for the offset that obtained in the \mbh-\smass\ correlations in Section~\ref{sec:mm}. We use green open circles to point out the shifting of the expected population given these biases, as shown in Figure~\ref{fig:MM-vz}.

@@

{\color{blue}
\subsection{The origin of the offset}
{\color{red}[Xuheng:  Given their larger uncertainty, do we still want to present these figures?]}
We seek for the cause that could raise the evolution in the BH and host galaxy correlations at high redshift. We consider if the offset is related to the AGN activities. The straightforward way is to study such offset, i.e. $\Delta \log \mathcal M_{\rm BH}$, as a function of \mbh\ and Eddington ratios, showing in Figure~\ref{fig:offset_vs_MBH_edd}. Interestingly, we visually see the trend that the offset turns to be larger with at value of \mbh. However, at higher Eddington ratio, the offset turns to be lower.
 {\color{red} Some interpretations need to be presented.}

@@

\subsection{Systematic with different local anchor}
To compare our high-$z$ sample to the local relation, we adopt the local measurements by \citet{Ben++10, Bennert++2011, H+R04}. In the literature, there are other local sample have been measured which also usually be considered as the local anchor. We note that different local samples have inconsistency which could change the result of the co-evolutions.

To estimate this effect, we compare our local \mbh-\smass\ sample to the local quiescent galaxies by \citet{Kormendy13} (hereafter K13). We find that K13's local \mbh-\smass\ relation would raise the anchor by $\sim$0.3~dex and totally erase the offset of $\Delta\log$\mbh. However, we also note that the \mbh-\sigstar\ relations in K13 is also higher than the one by our local sample. Note that the \mbh-\sigstar\ relations by the quiescent galaxy are usually used to determine the virial coefficient for AGNs. That is, adopting the K13 would boost the value of our \mbh\ by $\sim$0.3~dex as well. As a result, our inference of the fitted offset $\gamma$ still remains at the same level.

@@

Combining our high-$z$ measurements with the intermediate redshift samples from the literature~\citep{Park15, Bennert11, SS13, Cisternas2011}, we compared the scaling relations to the ones by the local with main results summarized as follows:
\begin{enumerate}
\item The \mbh-\smass\ relations at higher redshift are inconsistent with the local ones, i.e. Figure~\ref{fig:MM}, \ref{fig:MM-vz}.
\item Considering the correction for passive evolution of galaxy luminosity, the \mbh-\lhost\ relations at higher redshift are inconsistent with the local ones,  i.e. Figure~\ref{fig:ML-vz}.
\item The offsets of by the evolution are well described by the form $\Delta\log\mathcal M_{\rm BH}= \gamma \log (1 + z)$. Taking intro account selection effect, we obtain $\gamma = 0.8\pm0.3$ (\mbh-\smass) and $\gamma = 0.6\pm0.3$ (\mbh-\lhost).
\item We compare the properties of our active galaxy sample to the ones from inactive galaxy in the CANDLES imaging survey at the same redshift range, finding no significant discrepancy among them.
\end{enumerate}

Our inference indicates the evidence of disk+bluge component, i.e. the ones with \sersic\ $n<2$, and the local comparing samples are bulge dominated sample, we hence conclude that the BHs 8-10~Gyrs ago reside in bulges, if not entire galaxies, which are less massive/luminous than today.

@@

The authors fully appreciate the discussions with Hyewon Suh, Vardha N. Bennert, Anton M. Koekemoer, Takahiro Morishita and Peter Williams.
